

\input{packages.tex}

\moderncvtheme[blue]{casual}
\sethintscolumnlength{4cm}

\title{Curriculum Vitae}
\firstname{Christian}
\familyname{Döring}
\mobile{+4915163484441}
\email{christian.doering@tum.de}

\begin{document}

\maketitle


\section{Education}
\cventry{Sept. 2011 - June 2019}{Abitur (A-Levels)}{Gymnasium Bruckmühl}{}{}{}
\cventry{Since Oct. 2019}{B.Sc., Electrical and Computer Engineering}{Technical University of Munich}{}{}{}

\section{Internships}
\cventry{July 26 - Aug 28, 2021}{Developer}{Aurum GmbH}
{Munich}{}
{Development of an RFID/NFC interface Device for writing to protectable memory of IoT sensors.}
\cvlistitem{NFC protocol standard e.g. iso14443}
\cvlistitem{OOP like programming in C99}

\cventry{July 10 - July 14, 2017}{Intern, client support}{Electronic Theater Controls (ETC)}{Holzkirchen}{}{}{}
\cventry{July 17 - July 21, 2017}{}{Lauterbach GmbH}{Höhenkirchen-Siegertsbrunn}{}{}{}

\section{Technical Experience}
\cvline{AI controlled model car}{Implementation of a neural network in C++ for
	controlling a model car with a Raspberry Pi for a school project. \newline A
	model car was equipped with five ultrasonic sensors. Then the neural network
	was pre-trained using an evolutionary algorithm in a simulated environment. In
	the end this neural network was connected to the input sensors of the car as
	well as to the controls. Tests where conducted to evaluate the object avoidance
	capabilities of the vehicle.}
\cvline{Vulkan-rt}{Path tracer written in Rust using the
	\httplink[sceen-13]{https://github.com/attackgoat/screen-13} library as a Vulkan
	abstraction. It supports the Disney BSDF with Next Event Estimation.}

\section{Programming Languages}
\cvline{C++}{Experience in modern C++ as well as C89 and C99. I have written
	Several projects in C/C++ from high level graphics applications to low level
	microcontroller code.}
\cvline{Python}{Experience using python with PyTorch, Tensorflow and
	mitsuba for ML.}
\cvline{Rust}{Experience using Rust for GPGPU and graphics' programming. As
	Rust seems to be a promising new language for low and high level
	programming without some caveats of C++, I use it for my personal
	projects.}

\section{Other Abilities and Skills}
\subsection{Languages}
\cvlanguage{German}{native speaker}{}
\cvlanguage{English}{B2+/C1}{}



\end{document}

